Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed

### 2023-02-17 outputs/paper/paper.qmd
Edits

```{r setup}
#| echo: false
#| message: false
#| warning: false
# install.packages('readr')
# install.packages('here')
# install.packages("readstata13")  #  readstata13_0.9.2
# install.packages("MASS") # MASS_7.3-51.6  
# install.packages("sandwich")  # sandwich_2.5-1 
# install.packages("lmtest") # lmtest_0.9-37 
# install.packages("pBrackets") # pBrackets_1.0

library(readr) # read_csv
library(here) # here
library(readstata13) #  readstata13_0.9.2
library(MASS) # MASS_7.3-51.6  
library(sandwich)  # sandwich_2.5-1 
library(lmtest) # lmtest_0.9-37  
library(pBrackets) # pBrackets_1.0

#survey_data <- read_dta(here::here("inputs/data/survey_cleaned.csv"))
```

# Data

@@

# Discussion 
## Findings 
## Implications 
## Ethical Implications 
## Limitations 
## Future Research

>>>>

```{r setup}
#| echo: false
#| message: false
#| warning: false
# install.packages('readr')
# install.packages('here')
# install.packages("readstata13")  #  readstata13_0.9.2
# install.packages("MASS") # MASS_7.3-51.6  
# install.packages("sandwich")  # sandwich_2.5-1 
# install.packages("lmtest") # lmtest_0.9-37 
# install.packages("pBrackets") # pBrackets_1.0  
# install.packages("dplyr") 
# install.packages("tidyverse")

library(readr) # read_csv
library(here) # here
library(readstata13) #  readstata13_0.9.2
library(MASS) # MASS_7.3-51.6  
library(sandwich)  # sandwich_2.5-1 
library(lmtest) # lmtest_0.9-37  
library(dplyr)
library(tidyverse)
library(jtools)
library(huxtable)

survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))
```

# Data 
## Source
The paper used for replication is from the American Journal of Political Science which follows a discussion on the correlation of perceived mate competition and its contributions to anti-refugee sentiments and higher crime rates in Germany (cite paper). Our reproduction seeks to address two claims made from the original paper and apply a Canadian facing lens. The two claims are as follows: 
(1) Are non-immigrant German men who live in municipalities with excess male populations more likely to perceive refugees as threats?
(2) Are non-immigrant German men who perceive mate competition more likely to support violence as the only means to gain the attention of German politicians?
To collect this data, the original paper uses four waves of online survey data collected in Germany that are representative of gender, age and state (geographic location) [@main_paper].

## Methodology 
This paper will replicate the survey data that was originally collected for the 2021 paper by Dancygier, Egami, Jamal, and Rischkes, as previously mentioned. Using the online survey platform “Respondi”, they conduct four waves of surveys which spanned from September 2016 to December 2017 [@main_paper]. The researchers suggest that the anonymity provided by the online survey platform resulted in respondents answering more truthfully. [@main_paper]. To mitigate potential biases, the researchers employed list experiments in Waves 1 and 2, and in Wave 2, they randomly assigned 50% of the sample to either a control or treatment group. The treatment group was exposed to statements concerning their agreement with using violence against refugees as a means to get the attention of German politicians. However, no evidence was found to suggest that respondents were concealing their support for hate crimes when comparing the means of the control and treatment groups [@main_paper].

## Features

The original survey data assessed participants on 53 variables, being representative of gender, age and state. The range of recorded age data from the survey occurs from 19-89 years old. Age was then categorized by group which is as follows: 18-29, 30-39, 30-49, 50-59, and 60 and older. Both male and female participants took part in the survey, but females were only involved in the second and fourth waves of surveys. The survey was distributed across 16 German states. 
Our reproduction, however, included removing variables that were not utilized in our final reproduction analysis and included only the necessary Waves 2 and 4. As a part of our reproduction, we also simplified the names of variables to make them easier to work with. From the original data, each variable correlates with a survey question asked to participants. To discuss the variables used in our reproduction I have grouped them in the following way and have listed each variable below.

Sociodemographics:
* Age Group
* Gender
* State
* German Citizen 
* Marital Status 
* Relationship status, single
* Religious Affiliation 
* Education
* Occupation
* Income 
* Household Size 
* Subjective Social Status 
* Male population: determining states with access to males by dividing the number of women by men aged 14 and 44 for each municipality
* Politics: left and right-leaning 
* Politics: affiliated parties

Mate Competition: using a scale of agree or disagree
* Does the influx of male refugees make it difficult for non-immigrant german men to find female partners

Job Competition: using a scale of agree or disagree  
* The inflow of young make refugees make it more difficult for young non-immigrant German men to find work/ jobs

Life Satisfaction: scale of 0-10 
* Satisfaction with life

Encountering Refugees
* How many KM is the closest refugee reception center from your home 
* How many refugees do you believe have settled in your municipality in the last year 
* In the last month, how many refugees have you encountered in the following locations

Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree 
* Violence is sometimes the only means that citizens have to get the attention of German politicians 
* Attitudes towards Muslims
* Hostility against refugees justified
* Politicians should condemn attacks against refugees
* Racist violence is defensible if it leads to fewer refugees settling in a town 
* Attacks against refugee homes are sometimes necessary to make garner the attention of politicians 
* Refugee integration in Germany 
* German refugees should be entitled to German citizenship 
* The number of refugees should be reduced 
* Refugees are receiving more than non-immigrant Germans 
* Refugees should give up their culture to adopt that of Germany 
* Refugees are good for the economy 
* Refugees increase crime 
* Increased refugees increase the risk of terrorism 
* Will additional refugees in your town increase the influence of Islam (local)
* Will additional refugees in your town be a challenge for local schools (local)
* Will additional refugees in your town increase competition for housing (local) 
* Will additional refugees in your town change the way of life in your town (local)

Operational category 
* Experiement lists
* Treatement lists
* Outcome lists 
* Waves: out of 4

>>>>>>> b03039f (Create figure 1)

# Discussion 
## Findings 
## Implications 
## Ethical Implications 
=======
## Methodology
>>>>>>> b03039f (Create figure 1)

@@

# Discussion

## Findings

## Implications

## Ethical Implications

In their paper, Dancygier, Egami, Jamal, and Rischke examine the ethical implication of using experimental methodologies to investigate their research topic. By using descriptive data in the form of surveys they are able to investigate the opinions of non-immigrant German males and their perception of mate competition and its translation to anti-refugee violence. By avoiding experimental trials, they were able to explore their topic without provoking anti-refugee sentiment, which might have been a possible outcome had trials been conducted [@main_paper]. While conducting experimental trials on this topic of research is considered unethical, surveys and questionnaires may have a tendency to give respondents the impression that their opinions are commonly shared or even accurate. By being presented with a platform to express their perception of mate competition and if they agree that violence towards refugees is the only way to garner the attention of German politicians, respondents may feel that their opinions are incorrectly justified. This then has the potential to translate to violence towards German refugees.

## Accounting for Bias

Ethical implications and biases arise naturally when collecting quantitative and qualitative data. In their paper, Dancygier, Egami, Jamal, and Rischke use online survey platforms to assess if Germans living in areas with greater populations of men who experience turmoil in the mating market are more likely to perceive competition between themselves and refugees, moreover, does this ideology predict hate crime support [@main_paper]. The authors attempted to address ethical concerns and statistical biases by utilizing control groups and replicating their study with different samples and polling firms. However, one potential bias that is challenging to control for is the presence of sampling bias [@main_paper]. Sampling bias occurs when participants in a study are not representative of the estimand or the ideal population of interest. One method to control for this bias is simple random sampling, where participants are chosen by chance. Meaning that every individual in the population/ estimand has an equal chance of being selected. However, in their study, they were unable to utilize simple random sampling. Instead attempted to make their survey results representative by conducting four waves of surveys meant to be representative of age, gender and state/ geographical region [@main_paper}. Despite their effort, their survey results may not be entirely representative as individuals who have a strong interest in the subject matter are more likely to participate, meaning they do not reflect the views of all non-immigrant German males [@main_paper].

## Limitations

## Future Research

======= ##Figure 1 not including p value, percentage bar graph, detailed explanation of tercile meanings ======= ##Figure 1 not including p value, percentage bar graph, detailed explanation of tercile meanings

```{r}

```

```{r}
#| label: fig-excess
#| fig-cap: "look at deez"
#| echo: false
#| message: false
#| warning: false

survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))

# Subset of people from wave 4 and select needed columns
s_exc <- survey_data[survey_data$wave == 4 ,]
s_exc <- select(s_exc, c(gender, age, mate_compete, excess_males))
s_exc <- na.omit(s_exc)

# Add value for mate competition tercile
s_exc$matecomp <- ifelse(s_exc$mate_compete >= 3, 1, 0)
s_exc$terc <- ifelse(s_exc$excess_males < 1.04, "1st Tercile", ifelse(s_exc$excess_males < 1.12, "2nd Tercile", "3rd Tercile"))

# Create age groups for all people, men bw 18-44, and men bw 30-40
s_exc$agroup <- "All, Men & Women"

s_exc2 <- s_exc[s_exc$gender == "Male" & s_exc$age <= 44 & s_exc$age >= 18,]
s_exc2$agroup <- "Male 18-44"

s_exc3 <- s_exc[s_exc$gender == "Male" & s_exc$age <= 40 & s_exc$age >= 30,]
s_exc3$agroup <- "Male 30-40"

# Combining data frame back together
s_excm <- rbind(s_exc, s_exc2)
s_exct <- rbind(s_excm, s_exc3)

# Calculating proportion 
mean_all <- tapply(s_exc$matecomp, s_exc$terc, mean)
mean_2 <- tapply(s_exc2$matecomp, s_exc2$terc, mean)
mean_3 <- tapply(s_exc3$matecomp, s_exc3$terc, mean)

# Setting up data frame for plotting
s1 <- data.frame(c(mean_all))
colnames(s1) <- c("mean")
s2 <- data.frame(c(mean_2))
colnames(s2) <- c("mean")
s3 <- data.frame(c(mean_3))
colnames(s3) <- c("mean")

s_m <- rbind(s1, s2)
s_tot <- rbind(s_m, s3)

rownames(s_tot) <- NULL

s_tot$grp <- rep(c("All, Men & Women","Men 18-44","Men 30-40"),each=3)
s_tot$terc <- rep(c("1st Tercile","2nd Tercile","3rd Tercile"),times=3)

# Plotting
wrapper <- function(x, ...) 
{paste(strwrap(x, ...), collapse = "\n")}

s_tot %>% 
  ggplot(aes(x=terc, y=mean, group=grp, fill=grp)) +
  geom_col(position = "dodge")+
  labs(x="Terciles of Excess Male Rate", fill = "Group") +
  labs(y = wrapper("Proportion perceiving refugees as mate competition", width = 30)) +
  theme_minimal() +
  theme(legend.position="bottom") +
  theme(text=element_text(size=11, family="serif")) +
  ggtitle(wrapper("Nearly half of mating-aged men living in excess male areas perceive refugees as a threat to finding a partner", width =70)) +
  theme(plot.title = element_text(face = "bold"))
```

##Figure 2 add prevent bar

```{r}
#| label: fig-statements
#| fig-cap: "look at dat"
#| echo: false
#| message: false
#| warning: false

survey_w2 <- survey_data[survey_data$wave == 2,]

```

##Table 1 have it coded in completely (check marks), better description of meanings, labels of models (model1, model2,...)

```{r}
#| label: tbl-mate
#| fig-cap: "look at dat"
#| echo: false
#| message: false
#| warning: false

survey_w4 <- survey_data[survey_data$wave == 4,]

lm1 <- lm(only_means ~ mate_compete, data=survey_w4)
summary(lm1)

lm2 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction, data=survey_w4)
summary(lm2)

lm3 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction + 
            factor(age_group) +     # age group
            factor(gender) +     # gender 
            factor(state) +     # state  
            factor(citizenship) +    # german citizen
            factor(marital) +    # marital status
            factor(religion) +    # religious affiliation
            eduyrs +    # education
            factor(occupation) +    # main activity
            factor(income) +   # income
            factor(household_size) +   # household size
            factor(self_econ),    # subjective social status
          data=survey_w4)
summary(lm3)

lm4 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction + 
            factor(age_group) +   # age group
            factor(gender) +   # gender 
            factor(state) +   # state  
            factor(citizenship) +  # german citizen
            factor(marital) +  # marital status
            factor(religion) +  # religious affiliation
            eduyrs +  # education
            factor(occupation) +  # main activity
            factor(income) + # income
            factor(household_size) + # household size
            factor(self_econ) + # subjective social status
            factor(ref_integrating) + # Refugee Index (National-level; Q73) 8 in total
            factor(ref_citizenship) + factor(ref_reduce) + factor(ref_moredone) + factor(ref_cultgiveup) + 
            factor(ref_economy) + factor(ref_crime) + factor(ref_terror),
          data=survey_w4)
summary(lm4)

lm5 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction + 
            factor(age_group) +      # age group
            factor(gender) +      # gender 
            factor(state) +      # state  
            factor(citizenship) +     # german citizen
            factor(marital) +     # marital status
            factor(religion) +     # religious affiliation
            eduyrs + # education
            factor(occupation) +     # main activity
            factor(income) +    # income
            factor(household_size) +    # household size
            factor(self_econ) +    # subjective social status
            factor(ref_integrating) + # Refugee Index (National-level; Q73) 8 in total
            factor(ref_citizenship) + factor(ref_reduce) + factor(ref_moredone) + factor(ref_cultgiveup) + 
            factor(ref_economy) + factor(ref_crime) + factor(ref_terror) + 
            factor(ref_loc_services) +    # Refugee Index (Local, Q75)
            factor(ref_loc_economy) + factor(ref_loc_crime) + factor(ref_loc_culture) + factor(ref_loc_islam) + 
            factor(ref_loc_schools) + factor(ref_loc_housing) + factor(ref_loc_wayoflife), ## end
          data=survey_w4)
summary(lm5)

# Add More Variables 
# lrscale  Q21  Left-Right Scale
# afd, Q23  Closeness to AfD
# muslim_ind, afd_ind, contact_ind
# distance_ref Q71. Distance to refugee reception centers
# settle_ref Q72. Settlement of refugees living in area

formula.5 <- 
  as.character("only_means ~ mate_compete + job_compete + 
               life_satisfaction +  factor(age_group) + factor(gender) + 
               factor(state) + factor(citizenship) + factor(marital) + 
               factor(religion) + eduyrs + factor(occupation) + 
               factor(income) + factor(household_size) + factor(self_econ) + 
               factor(ref_integrating) + factor(ref_citizenship) + factor(ref_reduce) + 
               factor(ref_moredone) + factor(ref_cultgiveup) + 
               factor(ref_economy) + factor(ref_crime) + factor(ref_terror)  + 
               factor(ref_loc_services) +  factor(ref_loc_economy) + factor(ref_loc_crime) + 
               factor(ref_loc_culture) + factor(ref_loc_islam) + 
               factor(ref_loc_schools) + factor(ref_loc_housing) + factor(ref_loc_wayoflife)")

formula.6 <- paste(formula.5, "factor(distance_ref) + factor(settle_ref)", 
                   "left_right + afd + muslim_att + afd_att + contact_att", 
                   sep="+", collapse="+")

lm6 <- lm(as.formula(formula.6), data=survey_w4)
summary(lm6)

table1 <- export_summs(lm1, lm2, lm3, lm4, lm5, lm6, scale = TRUE, coefs = c('mate competition'='mate_compete', 'job competition'='job_compete', 'life satisfaction'='life_satisfaction')) |>
  set_escape_contents(FALSE) |>
  insert_row(c("sociodemographics \n", " ", " ", "X", "X", "X", "X"), after = 7) |>
  insert_row(c("national attitudes toward refugees", " ", " ", " ", "X", "X", "X"), after = 8) |>
  insert_row(c("local attitudes toward refugees", " ", " ", " ", " ", "X", "X"), after = 9) |>
  insert_row(c("additional controls", " ", " ", " ", " ", " ", "X"), after = 10)

table1

```
